Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2019-01-26 DingHickKritzMakRICAMChap.tex
new edits

%% Beginning of author included packages and defined macros
\usepackage{color,mathtools,bbm,xspace,natbib}
\usepackage{algorithm, algorithmicx}
\usepackage{algpseudocode}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\algnewcommand\algorithmicparam{\textbf{Parameters:}}
\algnewcommand\PARAM{\item[\algorithmicparam]}
\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
%\algnewcommand\STATE{\item}
\algnewcommand\RETURN{\State \textbf{Return }}

@@

There are many situations in which adaptive algorithms cannot perform much better than non-adaptive algorithms.  Yet, in practice adaptive algorithms are appreciated because they relieve the user from having to stipulate the computational effort required to achieve the desired accuracy.  Adaptive algorithms infer the computational effort required based on the function data sampled.

@@

\begin{algorithm}
	\caption{Non-Adaptive $\ALG$ for a Ball of Input Functions} \label{DHKM:BallAlg}
	\begin{algorithmic}
	\PARAM the ball radius, $R$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
	\INPUT a black-box function, $f$; an absolute error tolerance, $\varepsilon>0$

@@

Note that algorithms satisfying \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$. No matter how large a sample size is required by an algorithm, it is finite.  Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\SOL(f)}$ is arbitrarily large.  Thus, algorithms satisfying the error criterion only exist for some strict subset of $\calF$, and choosing that subset well is both an art and a science.

>>>>

%% Beginning of author included packages and defined macros
\usepackage{color,mathtools,bbm,xspace,natbib}
\usepackage{algpseudocode}
\usepackage{algorithm, algorithmicx}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\algnewcommand\algorithmicparam{\textbf{Parameters:}}
\algnewcommand\PARAM{\item[\algorithmicparam]}
\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
%\algnewcommand\STATE{\item}
\algnewcommand\RETURN{\State \textbf{Return }}

@@

In many situations, adaptive algorithms can be rigorously shown to perform \emph{essentially no better} than non-adaptive algorithms.  Yet, in practice adaptive algorithms are appreciated because they relieve the user from having to stipulate the computational effort required to achieve the desired accuracy.  Adaptive algorithms infer the computational effort required based on the function data sampled.  The key to resolving this seeming contradiction is to construct a theory based on assumptions that favor adaptive algorithms.  That is what we do here.

@@

\begin{algorithm}
\caption{Non-Adaptive $\ALG$ for a Ball of Input Functions \label{DHKM:BallAlg}}
	\begin{algorithmic}
	\PARAM the ball radius, $R$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
	\INPUT a black-box function, $f$; an absolute error tolerance, $\varepsilon>0$

@@

Note that algorithms satisfying \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$. Any algorithm must require a finite sample size, even if it is huge.  Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\SOL(f)}$ is arbitrarily large.  Thus, algorithms satisfying the error criterion only exist for some strict subset of $\calF$, and choosing that subset well is both an art and a science.
